---
title: "Pull Indicators for OECD countries from OECD Database"
author: "Brian Stacy"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 6, fig.cap = "&nbsp;")

# Written by Brian Stacy on October 29, 2020

library(tidyverse)
library(OECD)
library(here)
library(flextable)
library(wbgmaps)
library(wbggeo)
library(ggthemes)
library(httr)
library(jsonlite)
#set directories
dir <- here()

raw_dir <- paste(dir, '01_raw_data', sep="/")
output_dir <- paste(dir, '03_output_data', sep="/")


#read list of iso3c codes for matching from UN (https://unstats.un.org/unsd/methodology/m49/)
iso3c <- read_csv(paste(raw_dir,'iso_codes.csv', sep="/"),
                  col_types=list(col_character(), col_character(), col_character()))

span <- c(2004:2019)

#now create dataframe for merging from 2004 to 2019
iso_empty <- bind_rows(replicate(length(span), iso3c, simplify = FALSE), .id='date') %>%
  mutate(date=as.numeric(date)+span[1]-1) %>%
  select(iso3c, date, geoAreaCode) 


#get a list of oecd countries
oecd_country_query <-  GET(url = "https://api.worldbank.org/v2/country?region=OED&format=json") %>%
  content( as = "text", encoding = "UTF-8") %>%
  jsonlite::fromJSON( flatten = TRUE) 

#do some conversion to produce a dataframe
oecd_country_df <- oecd_country_query[[2]] %>%
  as_tibble() 
  
oecd_list <- oecd_country_df$id  #fill in the missing values for OECDs with 1s because by participating in OECD these countries have this


```


```{r programs, include=FALSE}


#Now map the result
quality = "high"
maps <- wbgmaps::wbgmaps[[quality]]

country_metadata <- wbstats::wbcountries()



spi_mapper  <- function(data, indicator, title) {
  
 indicator<-indicator

  map_df <- get(data) %>%
    filter(date==max(date, na.rm=T)) %>%
    group_by( iso3c) %>%
    #summarise(across(!! indicator,last)) %>%
    rename(data_available=!! indicator) %>%
    right_join(country_metadata) %>%
    mutate(data_available=if_else(is.na(data_available), as.numeric(NA), as.numeric(data_available)))    
  
  
   p1 <- ggplot() +
    geom_map(data = map_df, aes(map_id = iso3c, fill = 100*data_available), map = maps$countries) + 
    geom_polygon(data = maps$disputed, aes(long, lat, group = group, map_id = id), fill = "grey80") + 
    geom_polygon(data = maps$lakes, aes(long, lat, group = group), fill = "white")  +
     geom_path(data = maps$boundaries,
               aes(long, lat, group = group),
               color = "white",
               size = 0.1,
               lineend = maps$boundaries$lineend,
              linetype = maps$boundaries$linetype) +
    scale_x_continuous(expand = c(0, 0), limits = standard_crop_wintri()$xlim) +
    scale_y_continuous(expand = c(0, 0), limits = standard_crop_wintri()$ylim) +
  scale_fill_distiller(palette = "RdYlGn",
                       direction=1,
                       limits = c(0,100))  +
    coord_equal() +
    theme_map(base_size=12) +
    labs(
      title=str_wrap(title,100),
      subtitle= 'Data Point is for last year available (usually 2019)',
      caption = 'Source: SPI Indicator.',
      fill='SPI Indicator Value'
    )
  
  #add histogram by region 
  p2 <- map_df %>%
    group_by(region) %>%
    filter(region!='Aggregates') %>%
    mutate(Percentage=100*mean(data_available, na.rm=T),
           Label = paste(round(Percentage,0))) %>%
    ggplot(aes(x=Percentage, y=region, fill=region)) +
      geom_bar(stat="identity",position='dodge') +
      geom_text(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Region', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data',
      subtitle= 'Data Point is for last year available (usually 2019)'
      ) +
      expand_limits(x=c(0,100)) +
      theme_bw()

  #by income
    p3 <- map_df %>%
    group_by(income) %>%
    filter(region!='Aggregates') %>%
    mutate(Percentage=100*mean(data_available, na.rm=T),
           Label = paste(round(Percentage,0))) %>%
    ggplot(aes(x=Percentage, y=income, fill=income)) +
      geom_bar(stat="identity",position='dodge') +
      geom_text(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Income', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data',
      subtitle= 'Data Point is for last year available (usually 2019)'
      ) +
      expand_limits(x=c(0,100)) +
      theme_bw()
    
  # #add line graph over time
  p4 <- get(data)  %>%
    rename(data_available=!! indicator) %>%
    # right_join(spi_df_empty) %>%
    group_by( date) %>%
    mutate(data_available=if_else(is.na(data_available), as.numeric(NA), as.numeric(data_available))) %>%
    mutate(Percentage=100*mean(data_available),
           Label = paste(round(Percentage,0))) %>%
    ungroup() %>%
    ggplot(aes(y=Percentage, x=date)) +
      geom_point() +
      geom_line(fill='blue') +
      # geom_text_repel(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Date', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data'
      ) +
      expand_limits(y=c(0,100)) +
      theme_bw()
      
  print(p1)
  
  print(p2)
  
  print(p3)

  print(p4)
    
}


#define function to pull data from UN Stats and return
un_pull <- function(series,start, end) {
  # jsonlite::fromJSON(paste('https://unstats.un.org/SDGAPI/v1/sdg/Series/Data?seriesCode=',series,'&timePeriodStart=',start,'&timePeriodEnd=',end,'&pageSize=10000',sep=""), flatten = TRUE)$data %>%
      jsonlite::fromJSON(paste('https://unstats.un.org/SDGAPI/v1/sdg/Series/Data?seriesCode=',series,'&pageSize=10000',sep=""), flatten = TRUE)$data %>%

    as_tibble() %>%
    mutate(date=timePeriodStart) %>%
    right_join(iso3c)
    
}  
```

## Intro

In this project, we will pull indicator data from OECD database and judge OECD countries based on this data. Follow methodological approach in Measuring Distance to the SDG Targets 2019: An Assessment of Where OECD Countries Stand.

url: https://www.oecd.org/sdd/measuring-distance-to-the-sdg-targets-2019-a8caf3fa-en.htm

First, we will read in a csv file that I put together based on the metadata provided by the OECD on their approach.  Metadata is here: https://www.oecd.org/sdd/OECD-Measuring-Distance-to-SDGs-Targets-Metadata.pdf

The file provides a mapping, put together by the OECD, between the SDG targets and OECD indicators.  There are 132 targets that are mapped.

```{r mapping}
#read in csv with mapping between SDGs and OECD indicators
mapping_df_raw <- read_csv(paste0(raw_dir, "/OECD_SDG_mapping.csv"))

#get list of all OECD databases
dataset_list <- get_datasets()

#filter out the SDG targets where the OECD just used the UN database, since we already have these values.
mapping_df <- mapping_df_raw %>%
  filter(Source!="United Nations Global SDG Indicators Database") %>%
  mutate( database_id = case_when(#fix up some names and match to OECD database names
    grepl('Green',Source) ~ 'GREEN_GROWTH',
    grepl('Agri-Environmental', Source) ~ "AEI_NUTRIENTS",
    grepl('National Accounts',Source) ~ 'NAAG',
    grepl('Broadband',Source) ~ 'BROADBAND_DB',
    grepl('Creditor Reporting',Source) ~ 'CRS1',
    grepl('Fisheries Support',Source) ~ 'FISH_FSE',
    grepl('Government at a Glance',Source) ~ 'NAAG',
    grepl('General Government Accounts',Source) ~ 'NAAG',
    grepl('Better Life',Source) ~ 'BLI',
    grepl('Gender',Source) ~ 'GIDDB2019',
    grepl('Government at a Glance',Source) ~ 'GOV',
    grepl('OECD Education at Glance',Source) ~ 'EAG_TRANS',
    grepl('OECD Environment',Source) ~ 'ENV_KEI',
    grepl('Health',Source) ~ 'HEALTH_STAT',
    grepl('OECD ICT Access and Usage',Source) ~ 'ICT_HH2',
    grepl('IDD|Income',Source) ~ 'IDD',
    grepl('Labour',Source) ~ 'ALFS_POP_LABOUR',
    grepl('Main Science and Technology',Source) ~ 'MSTI_PUB',
    grepl('PIAAC ',Source) ~ 'EAG_AL',
    grepl('PISA',Source) ~ 'MSTI_PUB',
    grepl('Productivity',Source) ~ 'PDBI',
    grepl('SOCR',Source) ~ 'SOCR',
    grepl('TALIS',Source) ~ 'TALIS_IND',
    grepl('Time Use',Source) ~ 'TIME_USE',
    grepl('Transport',Source) ~ 'ITF_PASSENGER_TRANSPORT',
    grepl('TALIS',Source) ~ 'TALIS_IND'
  )
  )

database_list <- mapping_df %>%
  group_by(Source) %>%
  summarise(n=n(),
            database_id=first(database_id))

#loop through and pull metadata for each of the databases cited

for (variable in database_list$database_id) {
  
  dataset <- variable
  
  print(paste0(variable))
  tryCatch({

  dstruc <- get_data_structure(dataset)
  
  str(dstruc, max.level = 1)
  
  if (!file.exists(paste0(raw_dir,"/oecd_data/",variable,'_indicators.csv'))) {
    #get data
    temp_indicators <- get_dataset(variable,
                                start_time=2004,
                                end_time=2019) 
    
    write_excel_csv(temp_indicators,
                  paste0(raw_dir,"/oecd_data/",variable,'_indicators.csv') )
  }
  assign(paste0(variable,'_structure'), dstruc )
  

  
  # assign(paste0(variable,'_indicators'), temp_indicators )

  

}, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})


}


#read in UN data
un_sdg_df <- read_csv(paste(output_dir, '/un_sdg_df.csv',sep=""))

```


```{r oecd_pull, eval=FALSE, include=FALSE}


dataset <- 'SOCR'

dstruc <- get_data_structure(dataset)
str(dstruc, max.level = 1)

subjects <- dstruc$SUBJECT
times <- dstruc$TIME

df <- get_dataset(dataset = dataset, filter = filter_list)
head(df)

```


Next, using this mapping we will pull a select set of indicators from the OECD database.  

# SDG 1

```{r sdg1}

sdg1_map <- mapping_df %>%
  filter(grepl("^1\\.", SDG))

flextable(sdg1_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 1') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

```{r sdg1pull}

date_start <- 2015
date_end <- 2019

######
#1.2.1
variable <- 'IDD'

indicator_1.2.1 <- read_csv(paste0(raw_dir,"/oecd_data/",variable,'_indicators.csv')) %>%
  mutate(iso3c=LOCATION,
         date=obsTime) %>%
  filter(grepl('PVT', MEASURE)) %>%
  right_join(iso_empty) %>%
  filter(iso3c %in% oecd_list) %>%
  left_join(iso3c) %>%
  mutate(available=if_else(!is.na(obsValue),1,0)) %>%
  filter(between(date,date_start,date_end) ) %>%
  group_by(iso3c) %>%
  summarise(available=mean(available, na.rm=T)) %>%
  mutate(date=date_end)

spi_mapper('indicator_1.2.1','available', 'SDG 1.2.1 - OECD Data')

#pull from UNSD data to compare
indicator_1.2.1_UNSD <- un_sdg_df %>%
  filter(code=="1.2.1") %>%
  filter(iso3c %in% oecd_list) %>%
  filter(between(date,date_start,date_end) ) %>%
  left_join(iso3c) %>%
  group_by(iso3c) %>%
  summarise(ind_quality=mean(ind_quality, na.rm=T)) %>%
  mutate(date=date_end) 




spi_mapper('indicator_1.2.1_UNSD','ind_quality', 'SDG 1.2.1 - UNSD Data')

######
#1.3.1
variable <- "SOCR"

indicator_1.3.1 <- read_csv(paste0(raw_dir,"/oecd_data/",variable,'_indicators.csv')) %>%
    mutate(iso3c=COUNTRY,
         date=obsTime) %>%
  right_join(iso_empty) %>%
  filter(iso3c %in% oecd_list) %>%
  left_join(iso3c) %>%
  mutate(available=if_else(!is.na(obsValue),1,0)) %>%
  group_by(iso3c) %>%
  summarise(available=mean(available, na.rm=T)) %>%
  mutate(date=date_end)


spi_mapper('indicator_1.3.1','available', 'SDG 1.3.1 - OECD Data')

#pull from UNSD data to compare
indicator_1.3.1_UNSD <- un_sdg_df %>%
  filter(code=="1.3.1") %>%
  filter(iso3c %in% oecd_list) %>%
  filter(between(date,date_start,date_end) ) %>%
  left_join(iso3c) %>%
  filter(between(date,date_start,date_end) ) %>%
  group_by(iso3c) %>%
  summarise(ind_quality=mean(ind_quality, na.rm=T)) %>%
  mutate(date=date_end) 




spi_mapper('indicator_1.3.1_UNSD','ind_quality', 'SDG 1.3.1 - UNSD Data')

######
#1.a.2
variable <- "NAAG"

indicator_1.a.2 <- read_csv(paste0(raw_dir,"/oecd_data/",variable,'_indicators.csv')) %>%
    mutate(iso3c=LOCATION,
         date=obsTime) %>%
  filter(grepl('TLYCG', INDICATOR)) %>%
  right_join(iso_empty) %>%
  filter(iso3c %in% oecd_list) %>%
  left_join(iso3c) %>%
  filter(between(date,date_start,date_end) ) %>%
  mutate(available=if_else(!is.na(obsValue),1,0)) %>%
  group_by(iso3c) %>%
  summarise(available=mean(available, na.rm=T)) %>%
  mutate(date=date_end)


spi_mapper('indicator_1.a.2','available', 'SDG 1.a.2 - OECD Data')


#pull from UNSD data to compare
indicator_1.a.2_UNSD <- un_sdg_df %>%
  filter(code=="1.a.2") %>%
  filter(iso3c %in% oecd_list) %>%
  filter(between(date,date_start,date_end) ) %>%
  left_join(iso3c) %>%
  filter(between(date,date_start,date_end) ) %>%
  group_by(iso3c) %>%
  summarise(ind_quality=mean(ind_quality, na.rm=T)) %>%
  mutate(date=date_end) 




spi_mapper('indicator_1.a.2_UNSD','ind_quality', 'SDG 1.a.2 - UNSD Data')

```



# SDG 2

```{r sdg2}

sdg2_map <- mapping_df %>%
  filter(grepl("^2\\.", SDG))

flextable(sdg2_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 2') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 3

```{r sdg3}

sdg3_map <- mapping_df %>%
  filter(grepl("^3\\.", SDG))

flextable(sdg3_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 3') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 4

```{r sdg4}

sdg4_map <- mapping_df %>%
  filter(grepl("^4\\.", SDG))

flextable(sdg4_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 4') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 5

```{r sdg5}

sdg5_map <- mapping_df %>%
  filter(grepl("^5\\.", SDG))

flextable(sdg5_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 5') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```


# SDG 6

```{r sdg6}

sdg6_map <- mapping_df %>%
  filter(grepl("^6\\.", SDG))

flextable(sdg6_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 6') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 7

```{r sdg7}

sdg7_map <- mapping_df %>%
  filter(grepl("^7\\.", SDG))

flextable(sdg7_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 7') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 8

```{r sdg8}

sdg8_map <- mapping_df %>%
  filter(grepl("^8\\.", SDG))

flextable(sdg8_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 8') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 9

```{r sdg9}

sdg9_map <- mapping_df %>%
  filter(grepl("^9\\.", SDG))

flextable(sdg9_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 9') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 10

```{r sdg10}

sdg10_map <- mapping_df %>%
  filter(grepl("^10\\.", SDG))

flextable(sdg10_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 10') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 11

```{r sdg11}

sdg11_map <- mapping_df %>%
  filter(grepl("^11\\.", SDG))

flextable(sdg11_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 11') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 12

```{r sdg12}

sdg12_map <- mapping_df %>%
  filter(grepl("^12\\.", SDG))

flextable(sdg12_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 12') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 13

```{r sdg13}

sdg13_map <- mapping_df %>%
  filter(grepl("^13\\.", SDG))

flextable(sdg13_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 13') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 14

```{r sdg14}

sdg14_map <- mapping_df %>%
  filter(grepl("^14\\.", SDG))

flextable(sdg14_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 14') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 15

```{r sdg15}

sdg15_map <- mapping_df %>%
  filter(grepl("^15\\.", SDG))

flextable(sdg15_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 15') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 16

```{r sdg16}

sdg16_map <- mapping_df %>%
  filter(grepl("^16\\.", SDG))

flextable(sdg16_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 16') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

# SDG 17

```{r sdg17}

sdg17_map <- mapping_df %>%
  filter(grepl("^17\\.", SDG))

flextable(sdg17_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 17') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```


