---
title: "Pull Indicators for OECD countries from OECD Database"
author: "Brian Stacy"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 6, fig.cap = "&nbsp;")

# Written by Brian Stacy on October 29, 2020

library(tidyverse)
library(OECD)
library(here)
library(flextable)
library(wbgmaps)
#library(wbggeo)
library(ggthemes)
library(httr)
library(jsonlite)
library(readxl)
#set directories
dir <- here()

raw_dir <- paste(dir, '01_raw_data', sep="/")
output_dir <- paste(dir, '03_output_data', sep="/")


#read list of iso3c codes for matching from UN (https://unstats.un.org/unsd/methodology/m49/)
iso3c <- read_csv(paste(raw_dir,'iso_codes.csv', sep="/"),
                  col_types=list(col_character(), col_character(), col_character()))

span <- c(2004:2019)

#now create dataframe for merging from 2004 to 2019
iso_empty <- bind_rows(replicate(length(span), iso3c, simplify = FALSE), .id='date') %>%
  mutate(date=as.numeric(date)+span[1]-1) %>%
  select(iso3c, date, geoAreaCode) 


#get a list of oecd countries
oecd_country_query <-  GET(url = "https://api.worldbank.org/v2/country?region=OED&format=json") %>%
  content( as = "text", encoding = "UTF-8") %>%
  jsonlite::fromJSON( flatten = TRUE) 

#do some conversion to produce a dataframe
oecd_country_df <- oecd_country_query[[2]] %>%
  as_tibble() 
  
oecd_list <- oecd_country_df$id  #fill in the missing values for OECDs with 1s because by participating in OECD these countries have this




```


```{r api_indicators}
#Now we will pull data from the UN Stats API (https://unstats.un.org/SDGAPI/swagger/).  We will keep only the tier 1 indicators

#get a list of all SDG indicators
indicators_url <- 'https://unstats.un.org/SDGAPI/v1/sdg/Indicator/List?pageSize=10000'

#bring in the list of indicators
list_df <- jsonlite::fromJSON(indicators_url, flatten = TRUE) %>%
  as_tibble() %>%
  unnest(keep_empty = TRUE) %>%
  filter(tier==1) %>% # keep just the tier 1 indicators %>%
  group_by(code) %>%
  filter(row_number()==1) %>%
  select(goal, code, description)

```



```{r mapping_data}

#read in mapping data
mapping_df_raw <- read_csv(paste0(raw_dir, "/OECD_SDG_mapping.csv"))
#get list of all OECD databases
dataset_list <- get_datasets()

#filter out the SDG targets where the OECD just used the UN database, since we already have these values.
mapping_df <- mapping_df_raw %>%
  filter(Source!="United Nations Global SDG Indicators Database") %>%
  mutate( database_id = case_when(#fix up some names and match to OECD database names
    grepl('Green',Source) ~ 'GREEN_GROWTH',
    grepl('Agri-Environmental', Source) ~ "AEI_NUTRIENTS",
    grepl('National Accounts',Source) ~ 'NAAG',
    grepl('Broadband',Source) ~ 'BROADBAND_DB',
    grepl('Creditor Reporting',Source) ~ 'CRS1',
    grepl('Family', Source) ~ 'FAMILY',
    grepl('Fisheries Support',Source) ~ 'FISH_FSE',
    grepl('Government at a Glance',Source) ~ 'NAAG',
    grepl('General Government Accounts',Source) ~ 'NAAG',
    grepl('Better Life',Source) ~ 'BLI',
    grepl('Gender',Source) ~ 'GIDDB2019',
    grepl('Government at a Glance',Source) ~ 'GOV',
    grepl('OECD Education at Glance',Source) ~ 'EDU_ENRL_INST',
#    grepl('OECD Environment',Source) ~ 'ENV_KEI',
    grepl('Obesity',Indicator) ~ 'HEALTH_LVNG',
    grepl('Health',Source) ~ 'HEALTH_STAT',
    grepl('OECD ICT Access and Usage',Source) ~ 'ICT_HH2',
    grepl('IDD|Income',Source) ~ 'IDD',
    grepl('Labour',Source) ~ 'ALFS_POP_LABOUR',
    grepl('Main Science and Technology',Source) ~ 'MSTI_PUB',
    grepl('PIAAC ',Source) ~ 'EAG_AL',
    grepl('PISA',Source) ~ 'MSTI_PUB',
    grepl('Productivity',Source) ~ 'PDBI',
    grepl('SOCR',Source) ~ 'SOCR',
    grepl('TALIS',Source) ~ 'TALIS_IND',
    grepl('Time Use',Source) ~ 'TIME_USE',
    grepl('Transport',Source) ~ 'ITF_PASSENGER_TRANSPORT',
    grepl('TALIS',Source) ~ 'TALIS_IND'
  )
  )
```


```{r programs, include=FALSE}


#Now map the result
quality = "high"
maps <- wbgmaps::wbgmaps[[quality]]

country_metadata <- wbstats::wbcountries()



spi_mapper  <- function(data, indicator, title) {
  
 indicator<-indicator

  map_df <- get(data) %>%
    filter(date==max(date, na.rm=T)) %>%
    group_by( iso3c) %>%
    #summarise(across(!! indicator,last)) %>%
    rename(data_available=!! indicator) %>%
    right_join(country_metadata) %>%
    mutate(data_available=if_else(is.na(data_available), as.numeric(NA), as.numeric(data_available)))    
  
  
   p1 <- ggplot() +
    geom_map(data = map_df, aes(map_id = iso3c, fill = 100*data_available), map = maps$countries) + 
    geom_polygon(data = maps$disputed, aes(long, lat, group = group, map_id = id), fill = "grey80") + 
    geom_polygon(data = maps$lakes, aes(long, lat, group = group), fill = "white")  +
     geom_path(data = maps$boundaries,
               aes(long, lat, group = group),
               color = "white",
               size = 0.1,
               lineend = maps$boundaries$lineend,
              linetype = maps$boundaries$linetype) +
    scale_x_continuous(expand = c(0, 0), limits = standard_crop_wintri()$xlim) +
    scale_y_continuous(expand = c(0, 0), limits = standard_crop_wintri()$ylim) +
  scale_fill_distiller(palette = "RdYlGn",
                       direction=1,
                       limits = c(0,100))  +
    coord_equal() +
    theme_map(base_size=12) +
    labs(
      title=str_wrap(title,100),
      subtitle= 'Data Point is for last year available (usually 2019)',
      caption = 'Source: SPI Indicator.',
      fill='SPI Indicator Value'
    )
  
  #add histogram by region 
  p2 <- map_df %>%
    group_by(region) %>%
    filter(region!='Aggregates') %>%
    mutate(Percentage=100*mean(data_available, na.rm=T),
           Label = paste(round(Percentage,0))) %>%
    ggplot(aes(x=Percentage, y=region, fill=region)) +
      geom_bar(stat="identity",position='dodge') +
      geom_text(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Region', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data',
      subtitle= 'Data Point is for last year available (usually 2019)'
      ) +
      expand_limits(x=c(0,100)) +
      theme_bw()

  #by income
    p3 <- map_df %>%
    group_by(income) %>%
    filter(region!='Aggregates') %>%
    mutate(Percentage=100*mean(data_available, na.rm=T),
           Label = paste(round(Percentage,0))) %>%
    ggplot(aes(x=Percentage, y=income, fill=income)) +
      geom_bar(stat="identity",position='dodge') +
      geom_text(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Income', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data',
      subtitle= 'Data Point is for last year available (usually 2019)'
      ) +
      expand_limits(x=c(0,100)) +
      theme_bw()
    
  # #add line graph over time
  p4 <- get(data)  %>%
    rename(data_available=!! indicator) %>%
    # right_join(spi_df_empty) %>%
    group_by( date) %>%
    mutate(data_available=if_else(is.na(data_available), as.numeric(NA), as.numeric(data_available))) %>%
    mutate(Percentage=100*mean(data_available),
           Label = paste(round(Percentage,0))) %>%
    ungroup() %>%
    ggplot(aes(y=Percentage, x=date)) +
      geom_point() +
      geom_line(fill='blue') +
      # geom_text_repel(aes(label=Label)) +
      labs(
      title=str_wrap(paste(title, 'By Date', sep=" - "),100),
      caption = 'Source: SPI Indicators Raw Data'
      ) +
      expand_limits(y=c(0,100)) +
      theme_bw()
      
  print(p1)
  
  print(p2)
  
  print(p3)

  print(p4)
    
}


#define function to pull data from UN Stats and return
un_pull <- function(series,start, end) {
  # jsonlite::fromJSON(paste('https://unstats.un.org/SDGAPI/v1/sdg/Series/Data?seriesCode=',series,'&timePeriodStart=',start,'&timePeriodEnd=',end,'&pageSize=10000',sep=""), flatten = TRUE)$data %>%
      jsonlite::fromJSON(paste('https://unstats.un.org/SDGAPI/v1/sdg/Series/Data?seriesCode=',series,'&pageSize=10000',sep=""), flatten = TRUE)$data %>%

    as_tibble() %>%
    mutate(date=timePeriodStart) %>%
    right_join(iso3c)
    
}  
```

## Intro

In this project, we will pull indicator data from OECD database and judge OECD countries based on this data. Follow methodological approach in The Short and Winding Road to 2030: Measuring Distance to the SDG Targets, published in April 2022.

url: https://www.oecd.org/wise/measuring-distance-to-the-sdgs-targets.htm

First, we will read in a csv file that I put together based on the metadata provided by the OECD on their approach.  Metadata is here: https://www.oecd.org/sdd/OECD-Measuring-Distance-to-SDGs-Targets-Metadata.pdf

The file provides a mapping, put together by the OECD, between the SDG targets and OECD indicators.  There are 132 targets that are mapped.


Next, using this mapping we will pull a select set of indicators from the OECD database.  We retrieved a spreadsheet containing the indicator values and metadata for  OECD countries from the OECD website.  


# Read in Data

Next, we will pull the data from each country based on the OECD SDG report.

```{r read_data}

goal_1_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-2-people.xlsx"),
                        sheet="Goal 1")
goal_2_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-2-people.xlsx"),
                        sheet="Goal 2")
goal_3_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-2-people.xlsx"),
                        sheet="Goal 3")
goal_4_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-2-people.xlsx"),
                        sheet="Goal 4")
goal_5_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-2-people.xlsx"),
                        sheet="Goal 5")

goal_6_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-3-planet.xlsx"),
                        sheet="Goal 6")
goal_7_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-4-prosperity.xlsx"),
                        sheet="Goal 7")
goal_8_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-4-prosperity.xlsx"),
                        sheet="Goal 8")
goal_9_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-4-prosperity.xlsx"),
                        sheet="Goal 9")
goal_10_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-4-prosperity.xlsx"),
                        sheet="Goal 10")
goal_11_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-4-prosperity.xlsx"),
                        sheet="Goal 11")

goal_12_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-3-planet.xlsx"),
                        sheet="Goal 12")
goal_13_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-3-planet.xlsx"),
                        sheet="Goal 12")
goal_14_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-3-planet.xlsx"),
                        sheet="Goal 14")
goal_15_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-3-planet.xlsx"),
                        sheet="Goal 15")

goal_16_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-5-peace-and-partnerships.xlsx"),
                        sheet="Goal 16")
goal_17_df <- read_excel(path=paste0(raw_dir, "/oecd_data/data_2022/the-short-and-winding-road-to-2030-data-chapter-5-peace-and-partnerships.xlsx"),
                        sheet="Goal 17")


oecd_raw_df <- bind_rows(goal_1_df, goal_2_df, goal_3_df, goal_4_df, goal_5_df,
                         goal_6_df, goal_7_df, goal_8_df, goal_9_df, goal_10_df,
                         goal_11_df, goal_12_df, goal_13_df, goal_14_df, goal_15_df,
                         goal_16_df, goal_17_df) %>%
  rename(date=YEAR,
         code=Indicator,
         goal=Goal,
         target=Target,
         iso3c=iso3
         ) %>%
  mutate(goal=as.character(goal)) %>%
  right_join(list_df)


write_excel_csv(oecd_raw_df,
                file=paste(raw_dir,'/oecd_data/country_data/OECD_data_',Sys.Date(),',.csv', sep=""))

```



```{r data_clean}

oecd_df <- oecd_raw_df %>%
  select(iso3c, SeriesCode, value, date, code, goal) %>%
  filter(!is.na(code)) %>% #drop rows with no informatino on indicators
  filter(!is.na(iso3c))

oecd_fill_df <- oecd_df %>%
  complete(iso3c, code, date) %>% #rectangularize data to put data in country*indicator*year format
  filter(!is.na(date)) %>%
  mutate(ind_value=value, #form some variables matching what was done in UN SD database
         ind_quality=if_else(!is.na(ind_value),1,0),
         ind_metadata=SeriesCode
        ) %>%
  left_join(wbstats::wb_countries()) 
  

oecd_fill_df %>%
  select(iso3c, date, goal, code, ind_value, ind_quality, ind_metadata) %>%
  rename(ind_value.oecd=ind_value, 
         ind_quality.oecd=ind_quality, 
         ind_metadata.oecd=ind_metadata) %>%
  write_excel_csv(
                path=paste(raw_dir,'/oecd_data/country_data/OECD_data_scored_2022.csv', sep=""))
  
```

```{r saver}

#function to create scored data.  This is identical to the scoring used for the UN data


oecd_aki_fun <- function(date_start, date_end) {
  temp <- oecd_fill_df %>%
    filter(between(date,date_start,date_end) ) %>%
    filter(!is.na(ind_quality)) %>%
    group_by(iso3c, code, goal) %>%
    summarise(ind_quality=max(ind_quality, na.rm=T),
              ind_value=mean(ind_value, na.rm=T),
              ind_metadata=first(ind_metadata)) %>% #check if any values (even sub-indicators) for indicator
      mutate(ind_quality=if_else(is.na(ind_quality),0,ind_quality)) %>% # if the indicator is missing for a year in the database, set availability to 0.
      group_by(iso3c,goal) %>%
      summarise(ind_quality=round(mean(ind_quality),3) #get whether indicator exists at all in 5 years of this across countries
              ) %>%
    left_join(country_metadata) %>%
    filter(!is.na(region)) %>%
    select(iso3c, country,region, income, goal, ind_quality) %>%
    mutate(date=date_end)
  
  
  temp %>%
    select(iso3c,date, country,region, income, goal,ind_quality) %>%
    pivot_wider(names_from = 'goal',
                values_from='ind_quality',
                names_glue = "SPI.D3.{goal}")
}


####
# 10 Year window
####
#create this database for each year from 2004 to 2019 using a 5 year average
for (i in c(2016:2019)) {
  
  start=i-9
  end=i
  
  temp_df <- oecd_aki_fun(start,end)
  assign(paste('oecd_aki_',end, sep=""), temp_df)
}

if (exists('oecd_aki')) {
  rm('oecd_aki')
}
#now append together and save
for (i in c(2016:2019)) {
  
  temp<-get(paste('oecd_aki_',i, sep=""))
  
  if (!exists('oecd_aki')) {
    oecd_aki<-temp 
  } else {
    oecd_aki<-oecd_aki %>%
      bind_rows(temp) %>%
      arrange(-date, iso3c)
  }
}

write_excel_csv(oecd_aki, path=paste(output_dir, 'SPI_D3_OECD_data_10yr.csv', sep="/"))

####
# 8 Year window
####
#create this database for each year from 2004 to 2019 using a 5 year average
for (i in c(2016:2019)) {
  
  start=i-7
  end=i
  
  temp_df <- oecd_aki_fun(start,end)
  assign(paste('oecd_aki_',end, sep=""), temp_df)
}

if (exists('oecd_aki')) {
  rm('oecd_aki')
}
#now append together and save
for (i in c(2016:2019)) {
  
  temp<-get(paste('oecd_aki_',i, sep=""))
  
  if (!exists('oecd_aki')) {
    oecd_aki<-temp
  } else {
    oecd_aki<-oecd_aki %>%
      bind_rows(temp) %>%
      arrange(-date, iso3c)
  }
}

write_excel_csv(oecd_aki, path=paste(output_dir, 'SPI_D3_OECD_data_8yr.csv', sep="/"))

####
# 5 Year window
####
#create this database for each year from 2004 to 2019 using a 5 year average
for (i in c(2016:2019)) {
  
  start=i-4
  end=i
  
  temp_df <- oecd_aki_fun(start,end)
  assign(paste('oecd_aki_',end, sep=""), temp_df)
}

if (exists('oecd_aki')) {
  rm('oecd_aki')
}
#now append together and save
for (i in c(2016:2019)) {
  
  temp<-get(paste('oecd_aki_',i, sep=""))
  
  if (!exists('oecd_aki')) {
    oecd_aki<-temp
  } else {
    oecd_aki<-oecd_aki %>%
      bind_rows(temp) %>%
      arrange(-date, iso3c)
  }
}

write_excel_csv(oecd_aki, path=paste(output_dir, 'SPI_D3_OECD_data_5yr.csv', sep="/"))
####
# 3 Year window
####
#create this database for each year from 2004 to 2019 using a 5 year average
for (i in c(2016:2019)) {
  
  start=i-2
  end=i
  
  temp_df <- oecd_aki_fun(start,end)
  assign(paste('oecd_aki_',end, sep=""), temp_df)
}

if (exists('oecd_aki')) {
  rm('oecd_aki')
}
#now append together and save
for (i in c(2016:2019)) {
  
  temp<-get(paste('oecd_aki_',i, sep=""))
  
  if (!exists('oecd_aki')) {
    oecd_aki<-temp
  } else {
    oecd_aki<-oecd_aki %>%
      bind_rows(temp) %>%
      arrange(-date, iso3c)
  }
}

write_excel_csv(oecd_aki, path=paste(output_dir, 'SPI_D3_OECD_data_3yr.csv', sep="/"))

####
# 1 Year window
####
#create this database for each year from 2004 to 2019 using a 5 year average
for (i in c(2016:2019)) {
  
  start=i-0
  end=i
  
  temp_df <- oecd_aki_fun(start,end)
  assign(paste('oecd_aki_',end, sep=""), temp_df)
}

if (exists('oecd_aki')) {
  rm('oecd_aki')
}
#now append together and save
for (i in c(2016:2019)) {
  
  temp<-get(paste('oecd_aki_',i, sep=""))
  
  if (!exists('oecd_aki')) {
    oecd_aki<-temp
  } else {
    oecd_aki<-oecd_aki %>%
      bind_rows(temp) %>%
      arrange(-date, iso3c)
  }
}

write_excel_csv(oecd_aki, path=paste(output_dir, 'SPI_D3_OECD_data_1yr.csv', sep="/"))

```



# Annex

Below is a description of each OECD indicator and it's relation to the UN SDG indicators.

## SDG 1

```{r sdg1}

sdg1_map <- mapping_df %>%
  filter(grepl("^1\\.", SDG))

flextable(sdg1_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 1') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```


## SDG 2

```{r sdg2}

sdg2_map <- mapping_df %>%
  filter(grepl("^2\\.", SDG))

flextable(sdg2_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 2') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 3

```{r sdg3}

sdg3_map <- mapping_df %>%
  filter(grepl("^3\\.", SDG))

flextable(sdg3_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 3') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 4

```{r sdg4}

sdg4_map <- mapping_df %>%
  filter(grepl("^4\\.", SDG))

flextable(sdg4_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 4') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```




## SDG 5

```{r sdg5}

sdg5_map <- mapping_df %>%
  filter(grepl("^5\\.", SDG))

flextable(sdg5_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 5') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```


## SDG 6

```{r sdg6}

sdg6_map <- mapping_df %>%
  filter(grepl("^6\\.", SDG))

flextable(sdg6_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 6') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 7

```{r sdg7}

sdg7_map <- mapping_df %>%
  filter(grepl("^7\\.", SDG))

flextable(sdg7_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 7') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 8

```{r sdg8}

sdg8_map <- mapping_df %>%
  filter(grepl("^8\\.", SDG))

flextable(sdg8_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 8') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 9

```{r sdg9}

sdg9_map <- mapping_df %>%
  filter(grepl("^9\\.", SDG))

flextable(sdg9_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 9') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 10

```{r sdg10}

sdg10_map <- mapping_df %>%
  filter(grepl("^10\\.", SDG))

flextable(sdg10_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 10') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 11

```{r sdg11}

sdg11_map <- mapping_df %>%
  filter(grepl("^11\\.", SDG))

flextable(sdg11_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 11') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 12

```{r sdg12}

sdg12_map <- mapping_df %>%
  filter(grepl("^12\\.", SDG))

flextable(sdg12_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 12') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 13

```{r sdg13}

sdg13_map <- mapping_df %>%
  filter(grepl("^13\\.", SDG))

flextable(sdg13_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 13') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 14

```{r sdg14}

sdg14_map <- mapping_df %>%
  filter(grepl("^14\\.", SDG))

flextable(sdg14_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 14') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 15

```{r sdg15}

sdg15_map <- mapping_df %>%
  filter(grepl("^15\\.", SDG))

flextable(sdg15_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 15') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 16

```{r sdg16}

sdg16_map <- mapping_df %>%
  filter(grepl("^16\\.", SDG))

flextable(sdg16_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 16') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```

## SDG 17

```{r sdg17}

sdg17_map <- mapping_df %>%
  filter(grepl("^17\\.", SDG))

flextable(sdg17_map) %>%
  add_header_lines('Table: OECD Indicators for SDG 17') %>% 
  autofit() %>%
  theme_zebra() %>%
  align( align = "left", part = "body") %>%
  align_text_col()



```


